---
title: "DATA 605 Week 8 Homework"
author: "Yohannes Deboch"
date: "March 24/ 2019"
output:
  html_document: default
  username: root
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

### Chapter 7.2 Exercise 11 of Probability Text

11 A company buys 100 lightbulbs, each of which has an exponential lifetime of
1000 hours. What is the expected time for the first of these bulbs to burn
out? 

Answer:
Let $X_{1}, X_{2},...,X_{100}$ be 100 lightbulbs with exponential lifetime $\mu=1000$. The first lightbulb will fail at minimum value of $X_{j}$ suppose that is M. The denisity of M is exponential with mean $\mu/100$
```{r}
mu <- 1000
n <- 100
mu/n
```
The expected time for the first bulb to fail out is 10 hours with out disregading other factors that may  also influence  like electric grid and spikes.
 
### Chapter 7.2 Exercise 14 of the Probability Text

Assume that $X_1$ and $X_2$ are independent random variables, each having an
exponential density with parameter $\lambda$. Show that $Z = X_1-X_2$ has density
$f_Z(z) = (1/2)e^{-\lambda|z|}$.

#### Answer

$f_Z(z) = (1/2)e^{-\lambda|z|}$ can be re-written as $f_Z(z) = \begin{cases} (1/2)e^{-\lambda z}, & \mbox{if } z \ge 0, \\ (1/2)e^{\lambda z}, & \mbox{if }z <0. \end{cases}$

Since $X_1$ and $X_2$ have exponential density, in pdf format

<CENTER>
$f_{X_1}(x)=f_{X_2}(x)=\begin{cases} \lambda e^{-\lambda x}, & \mbox{if } x\ge 0, \\ 0, & \mbox{otherwise. }\end{cases}$
</CENTER>

$$
\begin{split}
  f_Z(z) &= f_{X_1+(-X_2)}(z) \\
    &= \int_{-\infty}^{\infty} f_{-X_2}(z-x_1) f_{X_1}(x_1) dx_1 \\
    &= \int_{-\infty}^{\infty} f_{X_2}(x_1-z) f_{X_1}(x_1) dx_1 \\
    &= \int_{-\infty}^{\infty} \lambda e^{-\lambda(x_1-z)} \lambda e^{-\lambda x_1} dx_1 \\
    &= \int_{-\infty}^{\infty} \lambda^2 e^{-\lambda x_1 + \lambda z} e^{-\lambda x_1} dx_1 \\
    &= \int_{-\infty}^{\infty} \lambda^2 e^{\lambda z - \lambda x_1 - \lambda x_1} dx_1 \\
    &= \int_{-\infty}^{\infty} \lambda^2 e^{\lambda(z-2x_1)} dx_1
\end{split}
$$

Consider $z=x_1-x_2$, then $x_2=x_1-z$.

If $z \ge 0$, then $x_2=(x_1-z) \ge 0$, and $x_1 \ge z$, and, using WolframAlpha, $f_Z(z) = \int_{z}^{\infty} \lambda^2 e^{\lambda(z-2x_1)} dx_1 = \frac{1}{2} \lambda e^{-\lambda z}$. 

If $z < 0$, then $x_2=(x_1-z) \ge 0$, and $x_1 \ge 0$, and $f_Z(z) = \int_{0}^{\infty} \lambda^2 e^{\lambda(z-2x_1)} dx_1 =\frac{1}{2} \lambda e^{\lambda z}$.

through merging the two we will have  $f_Z(z) = \begin{cases} (1/2)e^{-\lambda z}, & \mbox{if } z \ge 0, \\ (1/2)e^{\lambda z}, & \mbox{if }z <0. \end{cases}$

### Chapter 8.2 Exercise 1 of the Probability Text

Let $X$ be a continuous random variable with mean $\mu = 10$ and variance
$\sigma^2 = 100/3$. Using Chebyshev's Inequality, find an upper bound for the
following probabilities.

a. $P(|X - 10| \ge 2)$
b. $P(|X - 10| \ge 5)$
c. $P(|X - 10| \ge 9)$
d. $P(|X - 10| \ge 20)$

#### Answer

Chebyshev Inequality: $P(|X-\mu|\ge\epsilon) \le \frac{\sigma^2}{\epsilon^2}$ or, per example 8.4, $P(|X-\mu|\ge k\sigma) \le \frac{1}{k^2}$.

requiring a solution , $\mu=10$ and $\sigma = \sqrt{\frac{100}{3}} = \frac{10}{\sqrt{3}}$.

If $\epsilon = k\sigma$, then $k=\frac{\epsilon}{\sigma} = \frac{\epsilon\sqrt{3}}{10}$.

Let $u$ be upper bound in Chebyshev's Inequality, then $u = \frac{1}{k^2} = \frac{1}{(\epsilon\sqrt{3}/10)^2} = \frac{100}{3\epsilon^2}$.

a. $\epsilon=2$, the upper bound limit  is $u= \frac{100}{3\times 2^2} = \frac{25}{3} \approx 8.3333$. The upper bound is $1$ due to the fact that probability will not be greater than $1$.
b. $\epsilon=5$, the upper bound is $u= \frac{100}{3\times 5^2} = \frac{4}{3} \approx 1.3333$. Due to the fact that probability cannot be greater than $1$, the upper bound is $1$.
c. $\epsilon=9$, the value of the upper bound is $u= \frac{100}{3\times 9^2} = \frac{100}{243} \approx 0.4115$.
d. $\epsilon=20$, the upper bound is $u= \frac{100}{3\times 20^2} = \frac{1}{12} \approx 0.0833$.
